Simulating the Linux page cache in distributed applications with WRENCH

### 2020-12-09 paper_io_sim.tex
fixing paper structure and usage of latest IEEE template

\author{\IEEEauthorblockN{Hoang-Dung Do$^1$, Val\'erie Hayot-Sasson$^1$, Rafael Ferreira da Silva$^3$, Henri Casanova$^2$, Tristan Glatard$^1$
  }\\
  \IEEEauthorblockA{
    $^1$Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada\\
     $^2$Department of Information and Computer Sciences, University of Hawai‘i at Manoa, USA\\
     $^3$Department of Computer Science, University of Southern California, Los Angeles, USA
  }
}

@@

        \section{Acknowledgments}
The computing platform used in the experiments was obtained with funding
from the Canada Foundation for Innovation.
\bibliographystyle{plain}
\tristan{Check references, in particular capitalization}
\bibliography{citation}

>>>>

\author{
  \IEEEauthorblockN{
    Hoang-Dung Do\IEEEauthorrefmark{1},
    Val\'erie Hayot-Sasson\IEEEauthorrefmark{1},
    Rafael Ferreira da Silva\IEEEauthorrefmark{3},
    Henri Casanova\IEEEauthorrefmark{2},
    Tristan Glatard\IEEEauthorrefmark{1}
  }\\
  \IEEEauthorblockA{
    \IEEEauthorrefmark{1}Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada\\
    \IEEEauthorrefmark{2}Department of Information and Computer Sciences, University of Hawai‘i at Manoa, USA\\
    \IEEEauthorrefmark{3}Information Sciences Institute, University of Southern California, Marina Del Rey, CA, USA
  }
}

@@

        \section{Acknowledgments}
The computing platform used in the experiments was obtained with funding
from the Canada Foundation for Innovation.

\bibliographystyle{IEEEtran}
\tristan{Check references, in particular capitalization}
\bibliography{citation}
